### 2017-11-15 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add last 3 problems

\item  Problem 26, Chapter 6
\item  Problem 29, Chapter 6
\item  Problem 35, Chapter 6

\end{enumerate}
\end{document}

>>>>

\item  Problem 26, Chapter 6

\smallskip
\textbf{Solution:}
No. In fact, let $\{x_i\}$ be the sequence of rational numbers in $[0, 1]$, then for each $i$, there is an irrational number $y_i $, s.t.
$x_i < y_i < y_{i+1} $. Then
$$
TV(f) \ge \sum_{i=1}^{\infty}(|f(x_{i+1})-f(y_i)|+|f(y_i)-f(x_i)|) = \sum_{i=1}^{\infty}2 = \infty.
$$
Thus $f$ is not of bounded variation.

\bigskip
\item  Problem 29, Chapter 6

\smallskip
\textbf{Solution:}

(a). No. In fact, consider the subinterval $[0, 1]$, let $x_i = \frac{1}{\sqrt{n\pi}} $, and $P_n = \{0, x_{2n+1}, x_{2n},\cdots, x_1\} $, then
$$
V(f, P_n) = \frac{1}{\pi}(1+\frac{2}{2n+1}+\frac{2}{2n}+\cdots+\frac{2}{2}+\frac{2}{1}-\cos(1)).
$$
Since the sum is a harmonic series, which diverges, we know $f $ is not of bounded variation.

(b). Yes. Consider only the interval $[0, 1]$ since $g$ is an even function. Since $g\in\mathcal{C}^1 $ and is bounded on (0, 1), then 
$$
g'(x) = 2x\cos\frac{1}{x}+\sin\frac{1}{x},
$$
and $|g'(x)|\le 3 $, thus by the definition of Riemann integral, for any partition $P$,
$$
V(g, P) \le \int_{0}^{1}|g'|dx.
$$
Thus
$$
TV(g) \le\int_{0}^{1}|g'|dx \le 3.
$$
\bigskip
\item  Problem 35, Chapter 6

\smallskip
\textbf{Solution:}
First, we have
$$
f'(x) = \alpha x^{\alpha-1}\sin(\frac{1}{x^\beta})-\beta x^{\alpha-\beta-1}\cos(\frac{1}{x^\beta}).
$$
Since we know $f\in\mathcal{C}^1 $ and $|f|\le 1$ on $(0, 1)$, then according to the definition of Riemann integrals, for any partition $P$ of $[0, 1]$,
$$
V(f, P) \le\int_{0}^{1}|f'|dx \le \int_{0}^{1}\alpha x^{\alpha-1}+\beta x^{\alpha-\beta-1}dx.
$$
Since $\alpha > \beta > 0$, we have $\alpha-1 > -1$, $\alpha-\beta-1 > -1$, thus 
$$
TV(f) \le\int_{0}^{1}\alpha x^{\alpha-1}+\beta x^{\alpha-\beta-1}dx < \infty.
$$
When $\alpha \le \beta$, let $P_n = \{0, (\frac{n\pi}{2})^{-\beta}, \cdots, (\frac{\pi}{2})^{-\beta}\}$ be a partition of $[0, 1]$. Then
$$
V(f, P_n) = \sum_{i=1}^{n}(\frac{i\pi}{2})^{-\frac{\alpha}{\beta}} \ge \sum_{i=1}^{n}\frac{2}{i}\pi.
$$
Since this series is a harmonic series, thus it diverges, which means
$$
TV(f) = \infty.
$$
\end{enumerate}
\end{document}
